---
title: "Lab 0 - Hello R!"
author: "Oliver Hess"
date: "January 17th, 2023"
format: pdf
editor: visual
---

## Load Packages

```{r}
#| label: load-packages
#| message: false
library(tidyverse)
library(datasauRus)
```

## Exercise 1

(Type your answer to exercise #1 here. Note this exercise doesn't require any R code.

```{r}
view(datasaurus_dozen) 

datasaurus_dozen %>% 
  count(dataset) 

# using count(dataset) to see the indivudiaul variables, but this can be done with the distinct() function
```

1,846 rows, 3 columns

13 variables (away, bullseye, circle, dino, dots, h_lines, high_lines, slant_down, slant_up, star, wide_lines, v_lines, x_shape)

## Exercise 2

```{r}
# I'm not sure how to delete a chunk... sorry

```

(The answer for this exercise is given below, but you should clean up the narrative so it only includes what you want to turn in.)

First, let's plot the data in the dino dataset (we will cover **ggplot2** in much more depth next week):

```{r}
#| label: plot-dino
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) + 
  geom_point()
```

Next calculate the correlation between `x` and `y` in this dataset.

```{r}
#| label: cor-dino
dino_data %>%
  summarize(r = cor(x, y))

# the r value is -0.06447185	
```

Correlation between x and y is -0.06447185

## Exercise 3

(Add code and narrative here as needed. Note the code chunks below are labeled with `plot-circle` and `cor-circle` to provide spaces to place the code for plotting and calculating the correlation coefficient.)

(When you have finished, delete these instructions.)

```{r}
#| label: plot-circle
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle") 
ggplot(data = circle_data, mapping = aes(x = x, y = y)) + 
  geom_point()

circle_data %>% 
  summarize(r = cor(x,y))
```

Some more narrative can go here.

```{r}
#| label: cor-circle

# I calculated the r value in the previous chunk
# r for circle_data is -0.06834336

```

Conclude with some more narrative, if needed.

From my limited stats knowledge, the r value is how close the set of points is to a linear relationship. Clearly, a circle and a dinosaur image are not the most linear datasets. Therefore, the values stray from 1... but that's all I can explain so far.

## Exercise 4

(Add a labeled code chunk and narrative here. Insert code chunks using the "insert chunk" button (a green C with a +). Alternatively, use CMD + OPTION + I (Mac) or CTRL + ALT + I (Windows).)

```{r}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star") 

ggplot(data = star_data, mapping = aes(x = x, y = y)) + 
  geom_point()

star_data %>% 
  summarize(r = cor(x,y))
```

## Exercise 5

(Add a labeled code chunk and narrative here. Insert code chunks using the "insert chunk" button (a green C with a +). Alternatively, use CMD + OPTION + I (Mac) or CTRL + ALT + I (Windows).)

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")

datasaurus_dozen %>% 
  group_by(dataset) %>% 
  summarize(r = cor(x, y))
```
